ESRC SDAI Application - Understanding domestic abuse using Big Data

### 2019-07-05 case_for_support.tex
Anna update

 Her Majesty's Inspectorate of Constabulary and Fires \& Rescue Services (HMICFRS) oversees police forces in England Wales, and regularly inspects their responses to reported crime, including cases of domestic abuse. Their latest crime data integrity inspection of 32 police forces have found that 20 forces require significant improvements in their crime recording practices \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}. These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of domestic abuse-related  cases reported to the police, a majority of which would have qualified as a crime.

  To explore , as well as understanding its implications with regards to victims' trust in the CJS, we will limit our sample to those who have reported a specific type of domestic abuse incident (sexual, physical violence, harassment and stalking) in the past 12 months, according to the CSEW. First, we will run a multinomial logistic regression model with police force fixed effects, aiming to explain how the police action taken (no action, warning, arrest, charge) depend on the socio-economic characteristics of the victim. \textit{For example, it is possible that police forces are less likely to record a case if the victim has a substance dependency. Too speculative?} To complement this analysis and explore potential interactions, we will also investigate this question with a mixed effects random forest with police force clustering. Second, we will also investigate how victim's satisfaction with the police, and their perception of their personal security depends on the police action taken, and their socio-economic characteristics, using a logistic and a random forest statistical framework.

@@

The first extensive investigation of the demographic and socio-economic predictors of domestic abuse victimisation. An exploration of how police response to reported cases, victim satisfaction with the police and perception of security after reporting domestic abuse depend on victim characteristics.

>>>>

 Her Majesty's Inspectorate of Constabulary and Fires \& Rescue Services (HMICFRS) oversees police forces in England Wales, and regularly inspects their responses to reported crime, including cases of domestic abuse. Their latest crime data integrity inspection of 32 police forces have found that 20 forces require significant improvements in their crime recording practices \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}. These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of reported crimes that were domestic abuse-related.

 We will explore whether the extent of crime mis-recording depends on victim characteristics (e.g., a crime reported by a victim with a mental illness, substance dependency or language difficulties might be less likely to be recorded as a crime by the police). Using the CSEW, we will be able to tell whether the domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}. We will run a multinomial regression with police force fixed effects for each broad crime type (sexual, physical violence, harassment and stalking), predicting whether the police's response (no action, warning, arrest, charge) depends on the socio-economic characteristics of the victim. Using a fixed effects approach will tell us the relative importance of police force and victim characteristics in crime mis-recording. To complement this analysis and explore potential interactions between our explanatory variables, we will also investigate this question with a mixed effects random forest with police force clustering. Second, using the same statistical model for each type of crime, we will also investigate how victim's satisfaction with the police, and their perception of their personal security after reporting a crime depends on the police action taken, and their socio-economic characteristics.

@@

The first extensive investigation of the demographic and socio-economic predictors of domestic abuse victimisation. A deeper understanding of the characteristics of police mis-recording and its effect on victim's trust in the CJS.
